Best Practices for Alchemical Free Energy Calculations : v\versionnumber

### 2018-03-28 paper/manuscript.tex
refelct repository name change
DLM rough draft of most of assigned material

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% IMPORTANT USER CONFIGURATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\versionnumber}{0.1}  % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/michellab/best_practice_afec}}  %this should be the main github repository for this article

@@

\author[1*]{John D. Chodera}
\author[2*]{Antonia S. J. S. Mey}
\author[2*]{Julien Michel}
\author[3*]{David L. Mobley}
\author[4*]{Conor Parks}
\author[5*]{Julia E. Rice}
\author[6*]{Michael Shirts}
\affil[1]{Computational and Systems Biology Program, Memorial Sloan Kettering Cancer Center, New York NY 10065}
\affil[2]{Departments of Pharmaceutical Sciences and Chemistry, University of California, Irvine}
\affil[3]{EaStCHEM School of Chemistry, David Brewster road, Joseph Black Building, The King's Buildings, Edinburgh, EH9 3FJ, UK}
\affil[4]{I don't know my affiliation}
\affil[5]{I don't know my affiliation}

@@

%%%%%%%%%%%%%%%%%%%%
%              Prerequesites                %
%%%%%%%%%%%%%%%%%%%%
\section{Prerequisites}
\label{sec:pre}
Here you would identify prerequisites/background knowledge that are assumed by your work and your checklist which you view as critical, ideally giving links to good sources on these topics.
Checklists are normally focused on errors made by users with training and experience in molecular simulations, so you can assume a basic familiarity with the fundamentals of molecular simulations.

\section{Scope and Goals}
\label{sec:scope}
\begin{itemize}
\item Preparation (focused on aspects unique to alchemical free energies), execution, and analysis of:
\begin{itemize}
\item Transfer free energies (hydration free energies, partition coefficients, etc.)
\item Binding free energies
\end{itemize}
\item Not in scope:
\begin{itemize}
\item Advanced ligand binding topics such as:
\item Covalent inhibition
\item Association which is not 1:1
\item Endpoint free energy methods
\item PMF binding free energy methods
\item Force field choice: Should be a separate document (review)
\end{itemize}
\end{itemize}

@@

\item Determine whether you need to \textbf{handle multiple binding modes}: (Mobley)
\begin{itemize}
\item In absolute: Confine-and-release, BLUES
\item In relative (ugh!!)
\end{itemize}
\item Determine \textbf{stopping conditions}
Uncertainty-directed stopping criteria can ensure target uncertainty is achieved

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% IMPORTANT USER CONFIGURATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\versionnumber}{0.1}  % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/michellab/alchemical-best-practices}}  %this should be the main github repository for this article

@@

\author[1*]{John D. Chodera}
\author[2*]{Antonia S. J. S. Mey}
\author[2*]{Julien Michel}
\author[3*]{David L. Mobley}
\author[4*]{Conor Parks}
\author[5*]{Julia E. Rice}
\author[6*]{Michael Shirts}
\affil[1]{Computational and Systems Biology Program, Memorial Sloan Kettering Cancer Center, New York NY 10065}
\affil[2]{Departments of Pharmaceutical Sciences and Chemistry, University of California, Irvine}
\affil[3]{EaStCHEM School of Chemistry, David Brewster Road, Joseph Black Building, The King's Buildings, Edinburgh, EH9 3FJ, UK}
\affil[4]{I don't know my affiliation}
\affil[5]{I don't know my affiliation}

@@

%%%%%%%%%%%%%%%%%%%%
%              Prerequesites                %
%%%%%%%%%%%%%%%%%%%%
\section{Prerequisites}
\label{sec:pre}
%Here you would identify prerequisites/background knowledge that are assumed by your work and your checklist which you view as critical, ideally giving links to good sources on these topics.
%Checklists are normally focused on errors made by users with training and experience in molecular simulations, so you can assume a basic familiarity with the fundamentals of molecular simulations.

Before proceeding with this document, you are assumed to have a basic familiarity with the principles of molecular simulations, molecular dynamics simulations, statistical mechanics and thermodynamics, and so on.
This document focuses on aspects specific to alchemical free energy calculations, which remain an advanced topic within the molecular simulations area. 
Thus, if you are a beginner in the area of molecular simulations, not all background you need will be covered within the scope of this document. 
For example, we assume that you are able to set up and conduct a successful equilibrium molecular dynamics simulation of a particular thermodynamic state of a system interest as a prerequisite for this document.

\section{Scope and Goals}
\label{sec:scope}

This document focuses on preparation, execution, and analysis of alchemical free energy calculations, especially on aspects of the molecular simulations used here which are unique to alchemical calculations.
A particular focus is on calculation of transfer free energies (hydration free energies, partition coefficients, etc.) and binding free energies (absolute and relative).

Not within our scope are advanced ligand binding topics such as:

\begin{itemize}
\item Covalent inhibition
\item Association which is not 1:1
\item Endpoint free energy methods
\item PMF binding free energy methods
\end{itemize}

Additionally, the choice of force field (for protein, ligand, ions, cosolvents, or cofactors) is outside of the scope of this work; here, we focus on attempting to ensure successful alchemical free energy calculations given a particular choice of system and force field.

@@

\begin{enumerate}
\item Determine whether you need to \textbf{handle multiple binding modes}: (Mobley)
\begin{itemize}
\item In absolute: Confine-and-release, BLUES
\item In relative (ugh!!)
\end{itemize}
\item Determine \textbf{stopping conditions}
Uncertainty-directed stopping criteria can ensure target uncertainty is achieved
